---
title: "PSY 8712 Week 8 Project"
author: "Jessica Wang"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

## **Reproducible Image and Online Resources**
An image of this project as of *`r Sys.Date()`* can be accessed by clicking [clicking this link](https://mybinder.org/v2/gh/wan00967/psy8712-week8.git/HEAD?urlpath=rstudio).

An interactive web app is available by [clicking this link instead](https://wan00967.shinyapps.io/shiny_week8/).

## **Script Settings and Resources**
```{r setup, echo=TRUE, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

## **Data Import and Cleaning**
Imports and cleans the dataset, built off of previous week's project with changes to fit the current objectives
```{r}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(timeStart = as.POSIXct(timeStart, format = "%Y-%m-%d %H:%M:%S"), 
         timeSpent = as.numeric(difftime(timeEnd, timeStart, units = "mins"))) %>% 
  mutate(condition = recode_factor(condition, "A" = "Block A", "B" = "Block B", "C" = "Control")) %>%
  mutate(gender = recode_factor(gender,"M" = "Male", "F" = "Female")) %>%
  mutate(q5 = 6-q5) %>%
  mutate(across(q1:q10, as.numeric)) %>%
  mutate(avg16 = rowMeans(select(., q1:q6))) %>%
  mutate(avg810 = rowMeans(select(., q8:q10))) 
```

## **Visualization**
This section visualizes the relationships within the data
```{r visualization, echo=TRUE, message=FALSE}
week8_tbl %>% 
  select(q1:q6)

week8_tbl %>%
  ggplot(aes(x = avg16, y = avg810)) +
  geom_point() +
  geom_smooth(method = "lm", color = "purple", alpha = 0.2) +
  labs(x = "Mean Scores on Q1-Q6",
       y = "Mean Scores on Q8-Q10",
       title = "Scatterplot of Mean Scores with OLS Regression Line") 
```

## **Analysis**
This section analyzes the correlation between the mean scores on Q1-Q6 and Q8-Q10
```{r correlation_analysis, echo=FALSE, message=FALSE, results='asis'}
correlation_result <- cor.test(week8_tbl$avg16, week8_tbl$avg810)
cor_value <- correlation_result$estimate
p_value <- correlation_result$p.value

# Format correlation to two decimal places without leading zero if it's less than 1
formatted_cor <- sub("^0", "", sprintf("%.2f", cor_value))

cat("I observed a correlation of", formatted_cor, "between the mean scores on Q1-Q6 and Q8-Q10. The p-value of this correlation is", sprintf("%.3f", p_value), ". This suggests that there is a very weak, positive relationship between the mean scores of these two sets of questions. However, the high p-value indicates that this correlation is not statistically significant at conventional significance levels")
```

## **Data Export**
Making a skinny dataset without the unused columns.
```{r Data Export}
week8_tbl %>%
  select(timeEnd,gender,avg16,avg810) %>%
  saveRDS("../shiny_week8/data.rds")
```
